Detecting distributional differences between temporal granularities for exploratory time series analysis

### 2021-11-10 paper/main.Rmd
link update from gravitas to hakear

The authors thank the ARC Centre of Excellence for Mathematical and Statistical Frontiers [(ACEMS)](https://acems.org.au/home) for supporting this research. Sayani Gupta was partially funded by [Data61 CSIRO](https://data61.csiro.au/) during her PhD. The Github repository, [github.com/Sayani07/paper-hakear](https://github.com/Sayani07/paper-gravitas), contains all materials required to reproduce this article and the code is also available online in the supplemental materials. This article was created with R [@R-language], `knitr` [@knitr2015;@R-knitr] and `rmarkdown` [@rmarkdown2018;@R-rmarkdown]. Graphics are produced with `ggplot2` [@Wickham2009pk].

>>>>

The authors thank the ARC Centre of Excellence for Mathematical and Statistical Frontiers [(ACEMS)](https://acems.org.au/home) for supporting this research. Sayani Gupta was partially funded by [Data61 CSIRO](https://data61.csiro.au/) during her PhD. The Github repository, [github.com/Sayani07/paper-hakear](https://github.com/Sayani07/paper-hakear), contains all materials required to reproduce this article and the code is also available online in the supplemental materials. This article was created with R [@R-language], `knitr` [@knitr2015;@R-knitr] and `rmarkdown` [@rmarkdown2018;@R-rmarkdown]. Graphics are produced with `ggplot2` [@Wickham2009pk].
